### 2012-03-20 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

The proposed algorithm consists of the following four main steps, described in detail in the rest of the chapter.

\begin{enumerate}
\item Construction of a syntax tree. We use lexical and syntax analyses proposed in \cite{thesis_schejbal} and for each XQuery on input, we construct a data structure defined in \ref{DEF_syntax_tree}.
\item Static Analysis of expression types. The algorithm searches for expressions in the syntax trees and statically (without evaluation) determines their types.
\item Inference of built-in types. When the types of expressions are determined, selected forms of expression are utilized to infer types of elements and attributes.
\item Key discovery. The final step is an extension of approach \cite{Necasky:2009:DXK:1529282.1529414} inferring keys and foreign keys.
\end{enumerate}

>>>>

\begin{figure}
\label{FIG_steps_algorithm}
\caption{Steps of the proposed algorithm.}
\includegraphics[scale=1]{algorithm.eps}
\end{figure}

The proposed algorithm consists of the following four main steps, show in Figure \ref{FIG_steps_algorithm} and described in detail in the rest of the chapter.

\begin{enumerate}
\item \textbf{Construction of a syntax tree}. We use lexical and syntax analyses proposed in \cite{thesis_schejbal} and for each XQuery on input, we construct a data structure defined in \ref{DEF_syntax_tree}.
\item \textbf{Static Analysis of expression types}. The algorithm searches for expressions in the syntax trees and statically (without evaluation) determines their types.
\item \textbf{Inference of built-in types}. When the types of expressions are determined, selected forms of expression are utilized to infer types of elements and attributes.
\item \textbf{Key discovery}. The final step is an extension of approach \cite{Necasky:2009:DXK:1529282.1529414} inferring keys and foreign keys.
\end{enumerate}

As can be seen in Figure \ref{FIG_steps_algorithm}, step 4 is independent on step 3. They both depend on step 2.
